---
title: "code-1"
author: "Romeo Penheiro"
date: "06/05/2022"
output: html_document
---

```{r packages, include=FALSE}
if (!requireNamespace('xfun')) install.packages('xfun')
xf <- loadNamespace('xfun')

cran_packages <- c(
        "ggplot2", # To create graphs
        "dplyr", # To wrangle data
        "import", # To import data
        "here", # To generate relative paths
        "readr" # To read data

)

if (length(cran_packages) != 0) xf$pkg_load2(cran_packages)

# gh_repos <- c(
# 
#         
# )
# if (length(gh_repos) != 0) xf$install_github(gh_repos)

import::from(magrittr, '%>%')
```

# Import the data

```{r}
# Go to the data folder and retrieve the data
doctor <- readr::read_csv(file = (here::here("data", 
                                             "doctor-characteristic-data"))) 
sofa <- readr::read_csv(file = (here::here("data", 
                                           "patient-SOFA-trajectory-data")))

patient <- readr::read_csv(file = (here::here("data",
                                              "patient-characteristic-data-at-ICU-admission")))

doctor_360 <- readr::read_csv(file = (here::here("data",
                                                 "physician-360-degree-evaluation-data")))

```





```{r}
ggplot2::ggplot(patient, ggplot2::aes(x = DocID, fill = P8)) +
        ggplot2::geom_bar(position="fill") +
        ggplot2::scale_y_continuous(labels = scales::percent) +
        ggplot2::geom_hline(yintercept = 0.5)
```

```{r}
training <- dplyr::left_join(x = patient,
                 y = doctor[, c(1, 8)],
                 by = "DocID") 
# Training of the doctor affects mortality of patients?
ggplot2::ggplot(training, ggplot2::aes(x = M7, fill = P8)) +
        ggplot2::geom_bar(position="fill") +
        ggplot2::scale_y_continuous(labels = scales::percent) +
        ggplot2::geom_hline(yintercept = 0.5)
```


```{r}
# Primary diagnosis at intake affects mortality of patients?
ggplot2::ggplot(training, ggplot2::aes(x = P10, fill = P8)) +
        ggplot2::geom_bar(position="fill") +
        ggplot2::scale_y_continuous(labels = scales::percent) +
        ggplot2::geom_hline(yintercept = 0.5)
# Higher mortality in gastrointestinal and respiratory
```

```{r}
# Look at the descriptive of patient demographics by primary diagnosis
training %>%
        dplyr::group_by(P10) %>%
        dplyr::summarise(mean_Charlson_comorbidity = mean(P4),
                         median_Charlson_comorbidity = median(P4),
                         sd_Charlson_comorbidity = sd(P4),
                         mean_APACHE = mean(P5),
                         median_APACHE = median(P5),
                         sd_APACHE = sd(P5),
                         mean_SOFA = mean(P6),
                         median_SOFA = median(P6),
                         sd_SOFA = sd(P6)) %>%
        dplyr::ungroup()
# No significant difference in descriptive of patient demographics by primary diagnosis; especially in gastrointestinal and respiratory
# Next investigate P1, P2, P3
```


# Challenge: Develop valid quality indicators to evaluate the performance of critical care physicians

1. Does earlier appropriate medically expert diagnoses result in earlier expert interventions (such as resuscitation, and antibiotic treatment, which are known to decrease patient mortality rates)?
2. Does a physician who is an expert team leader/communicator/collaborator has the best outcomes?
3. Examine the variability between ICU physicians on the outcomes of their critically ill patients. Does some physicians have more critically ill patients than others?
4. Does the physician 360 evaluations explain any observed differences in patient outcomes?
5. Do physicians that work in a particular ICU have better outcome? 
